---
title: "Lists and Data Frames"
output:
  learnr::tutorial:
    progressive: true
    allow_skip: true
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(tidyverse)
library(gradethis)
knitr::opts_chunk$set()
tutorial_options(exercise.checker = gradethis::grade_learnr)
```

## <span style="color: teal;">Lists</span>

An `R list` is a recursive vector. It's a data structure consisting of a collection of _components_. The components can be of different types (ie character, numeric) disguised as model objects, data frames, list-columns within data frames, and more. 

For example, a list could be a collection of different types of vectors of different lengths, as seen below.
 
```{r}
list(a = 1:3, 
     b = "a string",
     c = pi,
     d = list(-1, -5)
     )
```

Components of the list are _numbered_. These components are also known as sub-litss and can be extracted using a double bracket. For example, you can reference the first element of a list with `[[1]]` as seen below.

```{r}
x <- list(a = 1:3,
          b = "a string",
          c = pi,
          d = list(-1, -5)
          )
x[[1]]
```

Components can also be referenced via their _names_. For example, the first element of the list below could be referenced by `[["a"]]`

```{r}
x[["a"]]
```

## <span style="color: teal;">Exercise</span>

Combine the following four vectors into a list.

```{r list, exercise = TRUE}
x <- c(10, 9, 4)
y <- 1
z <- c("string", "characters")
```

```{r list-check}
x <- c(10, 9, 4)
y <- 1
z <- c("string", "characters")
grade_result(
  pass_if(~ identical(.result, list(x, y, z)))
)
```

## <span style="color: teal;">Data frames</span>

A _data frame_ is a specific type of _list_ with the class `data.frame`. Tibbles are a specific subclass of `data.frame` and one of the unifying features of the tidyverse. 
Data frames consist of _rows_ and _columns_. 

For example, here is a data frame with three columns, `x`, `y`, and `z` each with four rows.

```{r}
data.frame(
  x = c(2, 4, 6, 8),
  y = c(10, 12, 14, 16),
  z = c(18, 20, 22, 24)
)
```

For example, here is a `tibble` data frame with three columns, `x`, `y`, and `z`.

```{r}
tibble(
  x = (1:5), 
  y = (1), 
  z = (x^ 2 + y)
)
```

## <span style="color: teal;">Exercise</span>

Create a data frame using the `data.frame()` function consisting of two variables, `x` and `y`, detailed below.

```{r dataframe, exercise = TRUE}
x <- c(1, 2, 3)
y <- c("do", "re", "mi")
```

```{r dataframe-check}
x <- c(1, 2, 3)
y <- c("do", "re", "mi")
grade_result(
  pass_if(~ identical(.result, data.frame(x = x, y = y)))
)
```

